Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/related_work.tex
Expanded on differences in related work.
From reviewer 8:

> The related work section should more strictly emphasize the difference
> of the work from previous work in the field.

I read through the related works section again and expanded on some of
the differences between our work and RedBlue consistency and explicit
consistency. I thought the differences in the other sections of the
related work were pretty clear.

\newcommand{\sieve}{\textsc{SIEVE}}
\textbf{RedBlue Consistency and \sieve.}
RedBlue consistency is a consistency model that sits between causal consistency
and linearizability~\cite{li2012making}.
%
With RedBlue consistency, every operation is manually labelled as either red or
blue. All operations are executed with causal consistency, but with the added
restrictions that red operations are executed in a single total order embedded
within the causal ordering.
%
In~\cite{li2012making}, Li et al.\ introduce invariant safety as a
sufficient (but not necessary) condition for RedBlue consistent objects to be
\invariantconfluent{}. Invariant safety is an analog of \invariantclosure{} for
an operation-based system model (as opposed to the state based system model
that we use). Li et al.\ develop sophisticated techniques for deciding
invariant safety that involve calculating weakest preconditions. These
techniques are complementary to our work and can be used to improve the
\invariantclosure{} subroutine used by our decision procedures.

@@

\textbf{Explicit Consistency.}
Explicit consistency~\cite{balegas2015towards} is a consistency model that
combines \invariantconfluence{} and causal consistency, similar to RedBlue
consistency with invariant safety. To determine if a workload is amenable to
explicitly consistent replication, Balegas et al.\ determine if all pairs of
transactions can be concurrently executed on the same start state without
violating the invariant~\cite{balegas2015towards}. Balegas et al.\ argue that
this is a sufficient condition for explicit consistency. It is similar to
criterion (3) in \thmref{LatticeProperty}. Balegas et al.\ also describe a
variety of techniques---like conflict resolution, locking, and escrow
transactions~\cite{o1986escrow}---that can be used to replicate workloads that
do not meet their sufficient conditions. As discussed in \secref{Evaluation},
simple forms of these techniques can be modelled with segmented
\invariantconfluence{}.

>>>>

\newcommand{\sieve}{\textsc{SIEVE}}
\textbf{RedBlue Consistency and \sieve.}
RedBlue consistency is a consistency model that sits between causal consistency
and linearizability~\cite{li2012making}.
%
With RedBlue consistency, every operation is manually labelled as either red or
blue. All operations are executed with causal consistency, but with the added
restrictions that red operations are executed in a single total order embedded
within the causal ordering.
%
In~\cite{li2012making}, Li et al.\ introduce invariant safety as a
sufficient (but not necessary) condition for RedBlue consistent objects to be
\invariantconfluent{}. Invariant safety is an analog of \invariantclosure{}.
In~\cite{li2014automating}, Li et al.\ develop sophisticated techniques for
deciding invariant safety that involve calculating weakest preconditions. These
techniques are complementary to our work and can be used to improve the
\invariantclosure{} subroutine used by our decision procedures.
%
In contrast with these techniques, our \invariantconfluence{} decision
procedures can determine the \invariantconfluence{} of objects that are
\emph{not} invariant safe.

@@

\textbf{Explicit Consistency.}
Explicit consistency~\cite{balegas2015towards} is a consistency model that
combines \invariantconfluence{} and causal consistency, similar to RedBlue
consistency with invariant safety. To determine if a workload is amenable to
explicitly consistent replication, Balegas et al.\ determine if all pairs of
transactions can be concurrently executed on the same start state without
violating the invariant~\cite{balegas2015towards}. Balegas et al.\ argue that
this is a sufficient condition for explicit consistency. It is similar to
criterion (3) in \thmref{LatticeProperty}. In our work, we take a step further
and explore sufficient \emph{and necessary} conditions for
\invariantconfluence{}.
%
Balegas et al.\ also describe a variety of techniques---like conflict
resolution, locking, and escrow transactions~\cite{o1986escrow}---that can be
used to replicate workloads that do not meet their sufficient conditions.
Segmented \invariantconfluence{} is a general-purpose formalism that can be
used to model simple forms of these techniques.
